---
title: "My First time seeing penguins"
author: "Haileigh Patterson"
date: "13/03/2022"
output: 
  pdf_document
---

```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(tidyverse)
# penguins <- read_csv("C:/Users/omcla/OneDrive/Documents/R/win-library/4.1/palmerpenguins/extdata/penguins.csv")
library(palmerpenguins) ## install using install.packages() if not already installed
library(ggplot2) ## install using install.packages() if not already installed
```

# Going to SEA LIFE Kelly Tarlton's 

In February I went to [Kelly Tarlton's](https://www.visitsealife.com/auckland/) and saw penguins for the first time with my friend Sian. 

I was *23 years old* when I first saw a **penguin** 

* They have the following penguins:
  * King Penguins
  + Gentoo Penguins

The price to see the penguins at Kelly Tarlton's is:

Age  | Price
------------- | -------------
Adult | $41.00
Child  | $29.00
~~Illegally entering~~  | ~~Free~~



## `R` code - Average flipper length evaluated and printed


```{r}
penguins_nafree <- penguins %>% drop_na()
summarise(penguins_nafree, avg_flipper_length = mean(flipper_length_mm))
``` 



### Average flipper length evaluated only


```{r, echo = FALSE}
penguins_nafree <- penguins %>% drop_na()
summarise(penguins_nafree, avg_flipper_length = mean(flipper_length_mm))
``` 

### Average body mass printed code only

```{r eval = FALSE}
penguins_nafree <- penguins %>% drop_na()
summarise(penguins_nafree, avg_flipper_length = mean(flipper_length_mm))
``` 


### Plot with code

```{r, warning = FALSE}
ggplot(penguins_nafree,aes(x = body_mass_g, y = flipper_length_mm, colour = species)) +
    geom_point() +
theme_bw() +
labs(title = "Flipper Length by Body Mass",
         x = "Body Mass (g)", 
         y = "Flipper Length (mm)")
```

### Plot only

```{r, warning = FALSE, echo=FALSE}
ggplot(penguins_nafree,aes(x = body_mass_g, y = flipper_length_mm, colour = species)) +
    geom_point() +
theme_bw() +
labs(title = "Flipper Length by Body Mass",
         x = "Body Mass (g)", 
         y = "Flipper Length (mm)")
```

### Plot with caption

```{r, warning = FALSE, echo=FALSE}
ggplot(penguins_nafree,aes(x = body_mass_g, y = flipper_length_mm, colour = species)) +
    geom_point() +
theme_bw() +
labs(title = "Flipper Length by Body Mass",
         x = "Body Mass (g)", 
         y = "Flipper Length (mm)")
```


